Proposed Solution

### 2017-01-22 CAV17/secs/limit.tex
did we try to get this paper rejected last time?

\para{Legal misconfigurations.}
While \app can check for diverse configuration errors without
human intervention, most of the existing proactive 
misconfiguration detection techniques,
including \app, cannot handle configuration errors
resulting from events that occurred during system runtime.
Such configuration errors are referred to as {\em legal misconfigurations}%
~\cite{yin11anempirical}. In particular, 
many parameter misconfigurations have 
perfectly legal types and values, 
but do not deliver the functionality intended by users. 
For example, after a website's traffic significantly increases,
the parameter {\tt key\_buffer\_size} in MySQL may not 
be able to handle increasingly more data traffic,
thus leading to outage of the whole system.
These cases are more difficult to detect by
automatic checkers and may require more user training or
better configuration design.
A potential solution is to combine existing misconfiguration diagnosis
tools, \eg, X-ray~\cite{attariyan12x-ray} 
and ConfAid~\cite{attariyan10automating},
with \app in order to enhance 
misconfiguration checking capability.

>>>>

\para{Legal misconfigurations.}
Most of the existing proactive misconfiguration detection techniques, cannot handle configuration errors resulting from events that occurred during system runtime.
Such configuration errors are referred to as {\em legal misconfigurations}~\cite{yin11anempirical}. 
In particular, many parameter misconfigurations have perfectly legal types and values, but do not deliver the functionality intended by users. 
For example, after a website's traffic significantly increases, the parameter {\tt key\_buffer\_size} in MySQL may not  be able to handle increasingly more data traffic,
   thus leading to outage of the whole system.
While \app does not explicitly use any runtime information, we are still able to detect such errors, for example Sec.~\ref{sec:motiv4}.
Since \app relies on the collective knowledge of the training set, as long as the training set is mostly correct with respect to legal misconfigurations, these can still be detected.
